Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-03 testbed.tex
more testbed

# Assign hostname found in nodes.csv
if [ ! -z $hostname ]; then
    echo $hostname > /etc/hostname
    hostname $hostname
fi
\end{lstlisting}
\FloatBarVrier

% Get the files
\begin{lstlisting}[]
wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
\end{lstlisting}
\FloatBarrier

Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
\begin{lstlisting}[]
line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
%$ line="bash /home/pi/.rasp_config/set_hostname"
%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>

@@

\subsection{Installation and Updating}

>>>>

# Assign hostname found in nodes.csv
if [ ! -z $hostname ]; then
    echo $hostname > /etc/hostname
    hostname $hostname
fi
\end{lstlisting}
\FloatBarrier

% Get the files
\begin{lstlisting}[]
$ wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
# unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
\end{lstlisting}
\FloatBarrier

Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
\begin{lstlisting}[]
# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
# sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
%$ line="bash /home/pi/.rasp_config/set_hostname"
%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>

@@

\subsection{Installation and Updating the image}
